analysis

### 2022-10-24 r-analysis/analysis.Rmd
added china
aktueller stand GHG per cap

@@

glimpse(china_and_regions)
# plotting

china_and_regions %>% 
  ggplot(.,aes(y=GHG_pc,fill=as.factor(region), x=year)) +
  geom_line(color="#636363",alpha=0.3) +
  theme_ghg()

>>>>

data_china<-data_countries %>% 
  filter(country=="China") %>% 
  rename(region = country)

@@

glimpse(china_and_regions)

# plotting

china_and_regions %>% 
   ggplot( aes(x=year, y=GHG_pc, group=region, color=region)) +
    geom_line() +
    theme_ghg()

#set order of vlaues

levels<-china_and_regions %>%
  filter(year==2019) %>% 
  arrange(desc(GHG_pc)) %>% 
  pull(region)

levels

levels<-c("China",levels[-4])

china_and_regions %>%
  filter(year==2019) %>%
  mutate(region=fct_relevel(region,levels)) %>% 
   ggplot(., aes(y=GHG_pc,x=region, fill=as.factor(region) )) + 
    geom_bar( stat = 'identity') +
    scale_fill_brewer(palette = "Set2") +
    theme(legend.position="none")
